MultiDataGrowthAssessPico

### 2023-12-07 Code/MultiDataGrowthAssessPico.Rmd
Fixed filepath

library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(photobiologyWavebands)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
#library(dplyr)
```

@@

%>%
    # select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              # "lognormOD720_Gompertz_param",
              # "lognormdeltaOD_Gompertz_param",
              # "OD720_logistic_param",
              # "OD720trunc_exp_param",
              # "deltaODtrunc_logistic_param",
              # "OD720trunc_logistic_param",
              # "deltaOD_logistic_param",
              # "deltaODtrunc_exp_param"
              # ))

>>>>

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(photobiologyWavebands)
library(tidyverse)

@@
